openTSNE: a modular Python library for t-SNE dimensionality reduction and embedding

### 2020-07-06 paper/policar2020-opentsne.tex
Incorporate feature list table

\begin{figure*}[htbp]
  \includegraphics[width=\textwidth]{benchmarks}
  \caption{\label{fig:benchmarks}We benchmark openTSNE (v0.4.3) against three
	popular open-source implementations including
	scikit-learn~\cite{pedregosa2011scikit} (v0.23.1),
	MulticoreTSNE~\cite{Ulyanov2016} (v0.1), and
	FIt-SNE~\cite{linderman2019fast} (v1.1.0). Benchmarks were run on a
	consumer-grade Intel Core i7-7700HQ processor found in laptop
	computers, and on a server-grade Intel Xeon E5-2650. To generate
	benchmark data sets of different sizes, we subsampled data from the 10X
	Genomics 1.3 million mouse brain data set five times, resulting in five
	different data sets for each size. In total, each implementation was
	run on 30 different data sets. Notice that openTSNE scales similarly to
	FIt-SNE, as they both use the same interpolation-based approximation
	scheme, while scikit-learn and MulticoreTSNE utilize the Barnes-Hut
	approximation.}
\end{figure*}

@@

\opentsne\ is a Python package that focuses on accessibility. We provide
precompiled binaries for all major Python versions on all major platforms,
making the installation process as seamless as possible. \opentsne\ can be
installed through the Python Package Index (PyPI) or through conda on the
conda-forge channel. \opentsne\ is designed to be familiar to Python users and
follows the \textsf{scikit-learn} API~\cite{sklearn_api}, which is well
established in the Python data science ecosystem. \opentsne\ implements
multi-threaded versions of both the Barnes-Hut and FIt-SNE approximation
schemes, allowing it to be used on data sets containing millions of data
points. While the Python virtual machine introduces some performance overhead,
the runtime is comparable to that of its pure C++ counterpart --
\textsf{FIt-SNE}. Finally, \opentsne\ is extensible. Its modular design enables
researchers to quickly experiment with different settings and easily
incorporate their own components into the software.

@@

\begin{table}
\caption{\label{tab:features}Feature list...}

>>>>

\begin{figure*}[htbp]
  \includegraphics[width=\textwidth]{benchmarks}
  \caption{\label{fig:benchmarks}We benchmark openTSNE (v0.4.3) against three
	popular open-source implementations from
	scikit-learn~\cite{pedregosa2011scikit} (v0.23.1),
	MulticoreTSNE~\cite{Ulyanov2016} (v0.1), and
	FIt-SNE~\cite{linderman2019fast} (v1.1.0). Benchmarks were run on a
	consumer-grade Intel Core i7-7700HQ processor found in laptop
	computers, and on a server-grade Intel Xeon E5-2650. To generate
	benchmark data sets of different sizes, we subsampled data from the 10X
	Genomics 1.3 million mouse brain data set five times, resulting in five
	different data sets for each size. In total, each implementation was
	run on 30 different data sets. Notice that openTSNE scales similarly to
	FIt-SNE, as they both use the same interpolation-based approximation
	scheme, while scikit-learn and MulticoreTSNE utilize the Barnes-Hut
	approximation.}
\end{figure*}

@@

\opentsne\ is a Python package that focuses on accessibility. We provide
precompiled binaries for all major Python versions on all major platforms,
making the installation process as seamless as possible. \opentsne\ can be
installed through the Python Package Index (PyPI) or through conda on the
conda-forge channel. \opentsne\ is designed to be familiar to Python users and
follows the \textsf{scikit-learn} API~\cite{sklearn_api}, which is well
established in the Python data science ecosystem. \opentsne\ implements
multi-threaded versions of both the Barnes-Hut and FIt-SNE approximation
schemes, allowing it to be used on data sets containing millions of data
points. While the Python virtual machine introduces some performance overhead,
the runtime is comparable to that of its pure C++ counterpart --
\textsf{FIt-SNE}. Finally, \opentsne\ is extensible. Its modular design enables
researchers to quickly experiment with different settings and easily
incorporate their own components into the software. We provide a full feature
list and comparison to other popular t-SNE implementations in
Table~\ref{tab:features}.

\begin{table}
\caption{\label{tab:features}We compare the feature list of \opentsne to three popular open-source implementations from scikit-learn~(v0.23.1), MulticoreTSNE (v0.1), and FIt-SNE (v1.1.0). The first section corresponds to packaging and distribution. A properly packaged library is easily accessible to users and can easily be included as a dependency in other software packages. The second section lists the two approximation schemes. The FIt-SNE approximation scheme is required for t-SNE to scale up to millions of data points. The final section provides a list of extensions and improvements to the standard t-SNE algorithm, many of which can produce markedly better visualizations than under default parameter settings.}

@@
